Do More Subdivisions in Wards Increase Voter Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-03 outputs/paper/paper.qmd
Formatting

#Voter turnout by ward
ggplot(data = finalized_voter_statistics, mapping = aes(x = turnout, y = n)) +
  geom_point(shape = 21, fill = '#0f993d', color = 'white', size = 3) +
  sm_statCorr() 
```
```

>>>>

#Voter turnout by ward
ggplot(data = finalized_voter_statistics, mapping = aes(x = turnout, y = n)) +
  geom_point(shape = 21, fill = '#0f993d', color = 'white', size = 3) +
  sm_statCorr() 
```
